### 2020-04-06 Strings2020/strings2/strings2.tex
Add corrections to strings2

	For a quantum version, redefine $j(z)$ with normal ordering, and we have:

@@

	\item Following the convention of \textit{Polchinski}, expand $X^\mu,b,c$ into modes $\alpha^\mu_n,b_n,c_n$, then a generic level 2 state of an open string can be created as\footnote{
		Reference: Bram M.~Wouters, \href{https://esc.fnwi.uva.nl/thesis/centraal/files/f1989820784.pdf}{\textit{BRST quantization and string theory spectra}}. 
	}:
	\begin{equation}
	\begin{aligned}
		\ket{\psi} = \big(
			&e_{\mu\nu}
				\alpha^\mu_{-1}
				\alpha^\nu_{-1}
			+ \beta_\mu
				\alpha^\mu_{-1} b_{-1}
			+ \gamma_\mu
				\alpha^\mu_{-1} c_{-1}
			\\ &\qquad
			+ \eta\,b_{-1} c_{-1}
			+ e_\mu \alpha^\mu_{-2}
			+ \beta\,b_{-2}
			+ \gamma\,c_{-2}
		\big)\,\ket{k;0}
	\end{aligned}
	\end{equation}
	Here $e_{\mu\nu}$ is chosen to be symmetric since $
		\alpha^\mu_{-1}
		\alpha^\nu_{-1}
	$ commutes. 
	By acting on $L_0$ (expanded in modes), we find that $
		m^2 = -k^2 = \frac{1}{\alpha'}
	$: massive.

	The BRST charge $
		Q = \frac{1}{2\pi i} \oint \pqty{
			\dd{z} j(z)
			- \dd{\bar{z}} \tilde{j}(z)
		}
	$ can also be expanded in modes; the physical states are firstly, $Q$-closed; i.e.
	\begin{equation}
		Q_B \ket{\psi} = 0
		\ \Longrightarrow\ %
		k^\mu e_{\mu\nu} = 0,\quad
		k^\mu e_\mu = 0,\quad
		\beta_\mu = \beta = 0,
	\end{equation}
	This is also the negative-norm states.

	On the other hand, $Q$-exact states generate gauge transformations; this gives:
	\begin{equation}
		\gamma_\nu
		\mapsto \gamma_\nu + k^\mu e_{\mu\nu},\quad
		\gamma
		\mapsto \gamma + k^\mu e_{\mu},\quad
		e_{\mu\nu}
		\mapsto e_{\mu\nu}
			+ \beta_\mu k_\nu
			+ \beta_\nu k_\mu,\quad
		e_\mu
		\mapsto e_\mu + \beta k_\mu
	\end{equation}
	Here $e_{\mu\nu},e_\mu,\beta_\mu,\beta$ are seen as arbitrary gauge parameters. For closed string the result can be obtained by the doubling trick, i.e.\ by introducing anti-holomorphic modes $\tilde{\alpha},\tilde{b},\tilde{c}$ and imposing reality conditions. The result is similar. \qedfull

@@

	To obtain a full expression, notice that for the above transformation to be a \textit{symmetry}, the action should be invariant under $X(z)\mapsto X'(z)$:
	\begin{equation}
		S' = S
		\ \Longrightarrow\ %
		\int \dd[2]{z}
			\pd X'^\mu \pdbar X'_\mu (z,\bar{z})
		\xlongequal{(*)} \int \dd[2]{z'}
			\pd' X'^\mu \pdbar' X'_\mu (z',\bar{z}')
		= \int \dd[2]{z}
			\pd X^\mu \pdbar X_\mu (z,\bar{z})
	\end{equation}
	Here at $(*)$ we use the diff-invariant property of the action. 
	Restore the anti-holomorphic component and insert \eqref{eq:dilaton_holomorphic}, then we find that in order to cancel the $\order{\epsilon^2}$ terms, we have to fix:
%	\begin{gather}
%		X'(z',\bar{z}') - \alpha'V
%		\simeq X(z,\bar{z})
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{z'}{z} + \dv{\bar{z}'}{\bar{z}}
%			},\\[1ex]
%		X\longmapsto
%		X'(z,\bar{z})
%		\simeq X\pqty\Big{
%				w^{-1}(z),\bar{w}^{-1}(\bar{z})
%			} + \alpha'V
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{w}{z} + \dv{\bar{w}}{\bar{z}}
%			},
%	\end{gather}
	\begin{equation}
		X'(z') - X(z)
		= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \order{\epsilon^3}
		}
	\end{equation}
	The above process can be done order by order, in the end we obtain that\footnote{
		I would like to thank Lucy Smith for helpful discussions. 
	}:
	\begin{equation}
	\begin{aligned}
		X'(z',\bar{z}') - X(z,\bar{z})
		&= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \frac{1}{3}\,(\pd\epsilon)^2
			- \cdots
		} + \pqty{\mrm{conjugate}} \\
		&= -\frac{\alpha' V}{2}\,
			\ln (1 + \pd\epsilon)
		+ \pqty{\mrm{conjugate}} \\[.5ex]
		&= -\frac{\alpha' V}{2}\,
			\ln \pqty{
				\dv{z'}{z}
				\dv{\bar{z}'}{\bar{z}}
			}
	\end{aligned}
	\end{equation}

	\item Perform the usual Noether's procedure on the free boson action, and we have:
	\begin{equation}
		\var{\mcal{L}}
		\propto \frac{1}{\alpha'} \pqty{
				\pd \var{X}^\mu \pdbar X_\mu
				+ \pd X^\mu \pdbar \var{X}_\mu
			}
		\sim \pdbar \epsilon \pqty{
			V^\mu \pd^2 X^\mu
			- \frac{1}{\alpha'}
				\pd X^\mu \pdbar X_\mu
		}
	\end{equation}
	Here we've plugged in the holomorphic part of $\var{X}^\mu$, used integration by parts to move $\pdbar$ before $\epsilon$, and collected the $\pdbar\epsilon$ coefficients. This gives:
	\begin{equation}
		T(z) = - \frac{1}{\alpha'}\,\normorder{
				\pd X^\mu \pdbar X_\mu\!
			} + V^\mu \pd^2 X^\mu
	\end{equation}

@@

	\item The background $B$ field given above is not single-valued on the $\psi$ circle. Note that we've encountered such difficulty in electromagnetism with a multi-valued $A^\mu(x)$. In fact, the resolution for this issue is very similar to Dirac's quantization of the magnetic monopole\footnote{
		Reference: J.~J.~Sakurai, \textit{Modern Quantum Mechanics}. 
	}: by allowing the action $S$ to be invariant modulo $2\pi$, since $
		e^{-(S + 2\pi i)} = e^{-S}
	$. More specifically, for $\psi\mapsto\psi + 2\pi$, we have:
	\begin{equation}
	\begin{aligned}
		2\pi i\, n = \Delta S
		&= \frac{1}{4\pi\alpha'}
		\int \dd[2]{\sigma}
			i\epsilon^{ab} 
			R^2\sin\theta\,\pqty{
				2\pi - 0
			}\,\pqty{
				\pdd{a} \theta\,
				\pdd{b} \phi
				- \pdd{a} \phi\,
				\pdd{b} \theta
			} \\[.5ex]
		&= i\,\frac{R^2}{\alpha'}
		\int \dd[2]{\sigma}
			\sin\theta\,\epsilon^{ab}\,
				\pdd{a} \theta\,
				\pdd{b} \phi
	\end{aligned}
	\end{equation}
	Choose $
		(\sigma^1,\sigma^2) = (\theta,\phi)
	$ while $
		\psi = \psi(\theta,\phi)
	$, then the integral is reduced to $
		\tilde{A}
		= \int \dd[2]{\sigma} \sin\theta
		= 2\pi R\tilde{\ell}
	$, where $\tilde{\ell}$ is the string length weighted by $\sin\theta$. This leads to the following quantization:
	\begin{equation}
		\frac{R^3 \tilde{\ell}}{\alpha'}
		= n \in\mbb{Z},\quad
		R = \pqty\big{
			{n\alpha'}\big/{\tilde{\ell}}
			\mspace{3.5mu}
		}^{1/3}
		\ge \pqty\big{
			{\alpha'}\big/{\ell}
			\mspace{2.5mu}
		}^{1/3}
	\end{equation}
	In particular, in string units: $\alpha' = \ell = 1$, we have $R\ge 1$.
	\qedfull
	\end{enumerate}

@@

	For conformal transformation $
		z\mapsto z + \epsilon(z),\ %
		\bar{z}\mapsto \bar{z}
			+ \bar{\epsilon}(\bar{z})
	$, we have:
	\begin{equation}
		\delta_\epsilon j(0)
		= -\operatorname*{Res}\limits_{z\to 0}
				\epsilon(z)\,
				T(z)\,j(0)
			-\operatorname*{Res}\limits_{\bar{z}\to 0}
				\bar{\epsilon}(\bar{z})\,
				\tilde{T}(\bar{z})\,j(0)
	\end{equation}
	Hence the $z^{-3},\bar{z}^{-3}$ coefficients of the OPE reflect the $
		\epsilon = z^2,\ %
		\bar{\epsilon} = \bar{z}^2
	$ transformation of $j$.  By comparing the Weyl transformations, this yields a total coefficient of $4Q$.

>>>>

	For a quantum version, redefine $j(z)$ with normal ordering\footnote{
		Normal ordering between $\ge 3$ operators is in fact \textit{not} associative; this directly leads to the ambiguity we are about to discover. See \textit{Di Francesco et al} for more detailed discussions. 
		Na\"ively, $\normorder{bc\,\pd c}_{\,(0)}$ is \textit{defined} as $b(0)\,c(z_1)\,\pd c(z_2)$ while $z_1,z_2\to 0$, with singular terms subtracted; however, different ways of taking the limit might lead to different results. For example, we can first take $z_1\to 0$ then $z_2\to 0$, or we can first take $z_1\to z_2$ then $z_2\to 0$. This two procedures will differ by $
			\frac{3}{2}\,\pd^2 c(z)
		$, which is precisely the correction we are about to find out. \sidenote{\textit{I suppose this is somehow related to topology, e.g.\ braid group?}}
	}, and we have:

@@

	\item Following the convention of \textit{Polchinski}, expand $X^\mu,b,c$ into modes $\alpha^\mu_n,b_n,c_n$, then a generic level 2 state of an open string can be created as\footnote{
		Reference: Bram M.~Wouters, \href{https://esc.fnwi.uva.nl/thesis/centraal/files/f1989820784.pdf}{\textit{BRST quantization and string theory spectra}}. 
	}:
	\begin{equation}
	\begin{aligned}
		\ket{\psi} = \big(
			&e_{\mu\nu}
				\alpha^\mu_{-1}
				\alpha^\nu_{-1}
			+ \beta_\mu
				\alpha^\mu_{-1} b_{-1}
			+ \gamma_\mu
				\alpha^\mu_{-1} c_{-1}
			\\ &\qquad
			+ \eta\,b_{-1} c_{-1}
			+ e_\mu \alpha^\mu_{-2}
			+ \beta\,b_{-2}
			+ \gamma\,c_{-2}
		\big)\,\ket{k;0}
	\end{aligned}
	\end{equation}
	Here $e_{\mu\nu}$ is chosen to be symmetric since $
		\alpha^\mu_{-1}
		\alpha^\nu_{-1}
	$ commutes. 
	By acting on $L_0$ (expanded in modes), we find that $
		m^2 = -k^2 = \frac{1}{\alpha'} = l_s
	$: massive.

	The BRST charge $
		Q = \frac{1}{2\pi i} \oint \pqty{
			\dd{z} j(z)
			- \dd{\bar{z}} \tilde{j}(z)
		}
	$ can also be expanded in modes; note that:
	\begin{equation}
		Q^2 = \frac{1}{2}\,\{Q,Q\}
		\propto \oint \frac{\dd{z}}{2\pi i} 
			\operatorname*{Res}\limits_{z'\to z}
			j(z')\,j(z) + \pqty{\mrm{conjugate}}
	\end{equation}
	Compared with the $jj$ OPE, we see that $Q$ is nilpotent iff.\ $D = 26$, i.e.\ the critical dimension of bosonic string theory. This condition is necessary for consistent BRST quantization.

	The physical states are firstly, $Q$-closed; i.e.
	\begin{equation}
		Q_B \ket{\psi} = 0
		\ \Longrightarrow\ %
		4l_s\,k^\mu e_{\mu\nu}
			+ l_s\,k_\nu\eta
			+ e_\nu = 0,\quad
		2\sqrt{2}\,l_s\,k^\mu
			+ e^\nu_\nu e_\mu = 0,\quad
		\beta_\mu = \beta = 0,
	\end{equation}
	This is also the negative-norm states.

	On the other hand, $Q$-exact states generate gauge transformations; this gives:
	\begin{equation}
		\gamma_\nu
		\mapsto \gamma_\nu
			+ \gamma'_\nu,\quad
		\gamma
		\mapsto \gamma
			+ \gamma',\quad
		\eta
		\mapsto \eta + \eta',\quad
		e_{\mu\nu}
		\mapsto e_{\mu\nu} + l_s\,\pqty{
			\beta'_\mu k_\nu
			+ \beta'_\nu k_\mu
		},
%		\quad
%		e_\mu
%		\mapsto e_\mu + \beta k_\mu\,l_s
	\end{equation}
	Here $
		\beta'_\mu,\gamma'_\nu,\gamma',\eta'
	$ are arbitrary gauge parameters. For closed string the result can be obtained by the doubling trick, i.e.\ by introducing anti-holomorphic modes $\tilde{\alpha},\tilde{b},\tilde{c}$ and imposing reality conditions. The result is similar. \qedfull

@@

	To obtain a full expression, notice that for the above transformation to be a \textit{symmetry}, the action should be invariant under $X(z)\mapsto X'(z)$:
	\begin{equation}
		S' = S
		\ \Longrightarrow\ %
		\int \dd[2]{z}
			\pd X'^\mu \pdbar X'_\mu (z,\bar{z})
		\xlongequal{(*)} \int \dd[2]{z'}
			\pd' X'^\mu \pdbar' X'_\mu (z',\bar{z}')
		= \int \dd[2]{z}
			\pd X^\mu \pdbar X_\mu (z,\bar{z})
	\end{equation}
	Here at $(*)$ we use the diff-invariant property of the action. 
	Restore the anti-holomorphic component and insert \eqref{eq:dilaton_holomorphic}, then we find that in order to cancel the $\order{\epsilon^2}$ terms, we have to fix:
%	\begin{gather}
%		X'(z',\bar{z}') - \alpha'V
%		\simeq X(z,\bar{z})
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{z'}{z} + \dv{\bar{z}'}{\bar{z}}
%			},\\[1ex]
%		X\longmapsto
%		X'(z,\bar{z})
%		\simeq X\pqty\Big{
%				w^{-1}(z),\bar{w}^{-1}(\bar{z})
%			} + \alpha'V
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{w}{z} + \dv{\bar{w}}{\bar{z}}
%			},
%	\end{gather}
	\begin{equation}
		X'(z') - X(z)
		= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \order{\epsilon^3}
		}
	\end{equation}
	The above process can be done order by order, in the end we obtain that\footnote{
		I would like to thank Lucy Smith for helpful discussions. A better recipe to find finite transformations is to consider its properties under composition, which will lead to some constraints that can be solved to obtain the result. 
	}:
	\begin{equation}
	\begin{aligned}
		X'(z',\bar{z}') - X(z,\bar{z})
		&= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \frac{1}{3}\,(\pd\epsilon)^2
			- \cdots
		} + \pqty{\mrm{conjugate}} \\
		&= -\frac{\alpha' V}{2}\,
			\ln (1 + \pd\epsilon)
		+ \pqty{\mrm{conjugate}} \\[.5ex]
		&= -\frac{\alpha' V}{2}\,
			\ln \pqty{
				\dv{z'}{z}
				\dv{\bar{z}'}{\bar{z}}
			}
	\end{aligned}
	\end{equation}

	\item Perform the usual Noether's procedure on the free boson action, and we have:
	\begin{equation}
		\var{\mcal{L}}
		\propto \frac{1}{\alpha'} \pqty{
				\pd \var{X}^\mu \pdbar X_\mu
				+ \pd X^\mu \pdbar \var{X}_\mu
			}
		\sim \pdbar \epsilon \pqty{
			V^\mu \pd^2 X^\mu
			- \frac{1}{\alpha'}
				\pd X^\mu \pdbar X_\mu
		}
	\end{equation}
	Here we've plugged in the holomorphic part of $\var{X}^\mu$, used integration by parts to move $\pdbar$ before $\epsilon$, and collected the $\pdbar\epsilon$ coefficients. This gives:
	\begin{equation}
		T(z) = - \frac{1}{\alpha'}\,\normorder{
				\pd X^\mu \pdbar X_\mu\!
			} + V^\mu \pd^2 X^\mu
	\end{equation}
\pagebreak[3]

@@

	\item The background $B$ field given above is not single-valued on the $\psi$ circle. Note that we've encountered such difficulty in electromagnetism with a multi-valued $A^\mu(x)$. In fact, the resolution for this issue is very similar to Dirac's quantization of the magnetic monopole\footnote{
		Reference: J.~J.~Sakurai, \textit{Modern Quantum Mechanics}. 
	}: by allowing the action $S$ to be invariant modulo $2\pi$, since $
		e^{-(S + 2\pi i)} = e^{-S}
	$.

	More specifically, for $\psi\mapsto\psi + 2\pi$, we have:
	\begin{equation}
	\begin{aligned}
		2\pi i\, n = \Delta S
%		&= \frac{1}{4\pi\alpha'}
%		\int \dd[2]{\sigma}
%			i\epsilon^{ab} 
%			R^2\sin\theta\,\pqty{
%				2\pi - 0
%			}\,\pqty{
%				\pdd{a} \theta\,
%				\pdd{b} \phi
%				- \pdd{a} \phi\,
%				\pdd{b} \theta
%			} \\[.5ex]
%		&= i\,\frac{R^2}{\alpha'}
%		\int \dd[2]{\sigma}
%			\sin\theta\,\epsilon^{ab}\,
%				\pdd{a} \theta\,
%				\pdd{b} \phi
		= \frac{i}{2\pi\alpha'}
			\,\Delta\! \int_\Sigma
				X^* B
		= \frac{i}{2\pi\alpha'}
			\,\Delta\! \int_{X(\Sigma)}
				B
		= \frac{i}{2\pi\alpha'}
			\,\Delta\! \int_M H
	\end{aligned}
	\end{equation}
	$B$ is a 2-form in $S^3$, $X^* B$ denotes its pullback to the worldsheet, and $X(\Sigma)\subset S^3$ denotes the embedding of $\Sigma$ into $S^3$. Note that $H$ is proportional to the volume form in $S^3$, hence we have:
	\begin{equation}
		\Delta\! \int_M H
		= 2R^2\,\Delta\! \mop{Vol}(M)
		= 2R^2\,\mbb{Z} \mop{Vol}(S^3)
		= 2R^2\,2\pi^2\,\mbb{Z}
		= 4\pi^2 R^2\,\mbb{Z}
	\end{equation}
%	Choose $
%		(\sigma^1,\sigma^2) = (\theta,\phi)
%	$ while $
%		\psi = \psi(\theta,\phi)
%	$, then the integral is reduced to $
%		\tilde{A}
%		= \int \dd[2]{\sigma} \sin\theta
%		= 2\pi R\tilde{\ell}
%	$, where $\tilde{\ell}$ is the string length weighted by $\sin\theta$. 
	This leads to the following quantization:
	\begin{equation}
%		\frac{R^3 \tilde{\ell}}{\alpha'}
		\frac{R^2}{\alpha'}
		= n \in\mbb{Z},\quad
		R \ge \sqrt{\alpha'}
%		R = \pqty\big{
%			{n\alpha'}\big/{\tilde{\ell}}
%			\mspace{3.5mu}
%		}^{1/3}
		\ge \pqty\big{
			{\alpha'}\big/{\ell}
			\mspace{2.5mu}
		}^{1/3}
	\end{equation}
	In particular, in string units: $
		\alpha'
%		= \ell
		= 1
	$, we have $R\ge 1$.
	\qedfull
	\end{enumerate}

@@

	For conformal transformation $
		z\mapsto z + \epsilon(z),\ %
		\bar{z}\mapsto \bar{z}
			+ \bar{\epsilon}(\bar{z})
	$, we have:
	\begin{equation}
		\delta_\epsilon j(0)
		= -\operatorname*{Res}\limits_{z\to 0}
				\epsilon(z)\,
				T(z)\,j(0)
			-\operatorname*{Res}\limits_{\bar{z}\to 0}
				\bar{\epsilon}(\bar{z})\,
				\tilde{T}(\bar{z})\,j(0)
	\end{equation}
	Hence the $z^{-3},\bar{z}^{-3}$ coefficients of the OPE reflect the $
		\epsilon = z^2,\ %
		\bar{\epsilon} = \bar{z}^2
	$ transformation of $j$.  By comparing the Weyl transformations\footnote{
		Note that $
			(\textit{Conformal}\,)
			= (\textit{Weyl}\,)
				+ (\textit{Translation}\,)
		$. 
	}, this yields a total coefficient of $4Q$.
